### 2022-08-02 paper/akweury/document.tex
update eval

@@

%% 5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l l l }
		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
		Mean  					& 20 & 5.43 & \\ 
		\hline
		Median					& 20 & 3.53 & \\ 
		\hline
		$ 5^\circ $ 			& 20 & 0.67 & \\
		\hline
		$ 11.5^\circ $ 			& 20 & 0.89 & \\
		\hline
		$ 22.5^\circ $ 			& 20 & 0.97 & \\
		\hline
		$ 30^\circ $ 			& 20 & 0.98 & \\
	\end{tabular}
	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
	\label{tab:high_resolution_eval}
\end{table}

>>>>

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_normal_SVD.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_normal_GCNN-512.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_normal_Trip-Net-512.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_error_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_22_error_GCNN-512.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/fancy_eval_14_error_Trip-Net-512.png}
		\caption{Trip-Net}
	\end{subfigure}

%% 5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l l l }
		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
		Mean  					& 8.88 & 5.43 & \\ 
		\hline
		Median					& 3.66 & 3.53 & \\ 
		\hline
		$ 5^\circ $ 			& 0.63 & 0.67 & \\
		\hline
		$ 11.5^\circ $ 			& 0.79 & 0.89 & \\
		\hline
		$ 22.5^\circ $ 			& 0.89 & 0.97 & \\
		\hline
		$ 30^\circ $ 			& 0.92 & 0.98 & \\
	\end{tabular}
	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
	\label{tab:high_resolution_eval}
\end{table}

\section{Training on Real-Dataset}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{l l l l }
		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
		Mean  					& 8.20 & 8.90 & 8.80\\ 
		\hline
		Median					& 4.87 & 5.82 & 5.66 \\ 
		\hline
		$ 5^\circ $ 			& 0.51 & 0.43 & 0.44 \\
		\hline
		$ 11.5^\circ $ 			& 0.79 & 0.78 & 0.78 \\
		\hline
		$ 22.5^\circ $ 			& 0.93 & 0.93 & 0.93 \\
		\hline
		$ 30^\circ $ 			& 0.96 & 0.96 & 0.96\\
	\end{tabular}
	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
	\label{tab:high_resolution_eval}
\end{table}
